TBA

### 2019-09-26 paper.tex
Added bib to paper file
Added results section

@@

Two groups of participants were recruited for the experiments. 
Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments. 
Both groups were given some time before the experiments to familiarise with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
To minimise the speed/accuracy biases in the results, we asked the participants to focus on finding the targets, without worrying about the time it took.

@@

@@

>>>>

\usepackage{cleveref}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{siunitx}

@@

Two groups of participants were recruited for the experiments on a volunteer basis. 
Group \textit{G1} consisted of 42 young adults with normal eyesight who were blindfolded for the experiments, and group \textit{G2} contained 12 people with severe visual impairments (18-55 years old, 40 male, 14 female). 
None of the participants had any hearing or other disabilities that could have influenced their performance in the experiments.
Each participant performed 3 sets of experiments each, with the 2 characterisation experiments preceding the final target-search experiment. 
Both groups were given some time before the experiment target-search experiment to familiarise themselves with the system, the audio signal's behaviour and the \SI{512}{\hertz} on-level tone. 
Furthermore, to minimise the speed/accuracy biases in the results for this experiment, we asked the participants to focus on finding the targets, without worrying about the time it took.

@@

\subsection{Sound Localisation}

\subsection{Pitch Discrimination}

@@

\bibliographystyle{plain}
\bibliography{bib}
